Two years of explicit CiTO annotations

### 2022-11-24 article.Rmd
s/BioRegistry/Bioregistry/
Added the two requested additional declarations
Removed a bit of reflection on use in the journal

The pilot consists of a couple of components and the editorial explains some of them [@Willighagen_2020].
The Citation Typing Ontology was selected to express the intention [@usesMethodIn:Shotton_2010],
the intention is expressed a compact identifier wrapped in square brackets, also called a
safe CURIE, standard proposed by the W3C in 2010 [@usesMethodIn:McCarron2010,@usesMethodIn:Wimalaratne_2018].
The *cito* prefix is registered in BioRegistry [@usesDataFrom:Hoyt2022].
The *bibnotes* concept of the Springer Nature publishing platform was used as carrier.
Authors are guided by a landing page consisting of a BMC Collection at
[https://www.biomedcentral.com/collections/cito](https://www.biomedcentral.com/collections/cito)
and author guidelines explaining to authors
how they can add the annotations with their favorite editor at
[https://jcheminform.github.io/jcheminform-author-guidelines/cito](https://jcheminform.github.io/jcheminform-author-guidelines/cito).

@@

Because many publishing platforms currently do not support display of citation level intention annotation,
the default model only provides the annotation in the bibliography. The choice was made to use the `bibnotes`
idea which allows giving additional notes to a reference in the bibliography. The CiTO Pilot uses
the *safe CURIE* standard, but the typesetting in the *Journal of Cheminformatics* has shown to be inconsistent,
even within single articles, suggesting additional training or guidance may be needed.

>>>>

The pilot consists of a couple of components and the editorial explains some of them [@Willighagen_2020].
The Citation Typing Ontology was selected to express the intention [@usesMethodIn:Shotton_2010],
the intention is expressed a compact identifier wrapped in square brackets, also called a
safe CURIE, standard proposed by the W3C in 2010 [@usesMethodIn:McCarron2010,@usesMethodIn:Wimalaratne_2018].
The *cito* prefix is registered in Bioregistry [@usesDataFrom:Hoyt2022].
The *bibnotes* concept of the Springer Nature publishing platform was used as carrier.
Authors are guided by a landing page consisting of a BMC Collection at
[https://www.biomedcentral.com/collections/cito](https://www.biomedcentral.com/collections/cito)
and author guidelines explaining to authors
how they can add the annotations with their favorite editor at
[https://jcheminform.github.io/jcheminform-author-guidelines/cito](https://jcheminform.github.io/jcheminform-author-guidelines/cito).

@@

Because many publishing platforms currently do not support display of citation level intention annotation,
the default model only provides the annotation in the bibliography. The choice was made to use the `bibnotes`
idea which allows giving additional notes to a reference in the bibliography. The CiTO Pilot uses
the *safe CURIE* standard, compatible with the typesetting in the *Journal of Cheminformatics*.
This makes is easier to text mine the annotations by downstream tools.
